On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 arity1.tex
Update arity1.tex

There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. There are beads having a free hand at (1,0) and (-1,0) to realize (b) and (e) in Fig.~\ref{fig:3bonds} before a bead $i-1$ is fixed at (0,0). One of these two beads may be a predecessor of a bead $i-1$, but at least one bead is not. A bead $i-1$ makes a hydrogen bond with one of these two beads which is not its predecessor when it is fixed at (0,0). That is, it is impossible to put three beads having a free hand at (-1,0), (0,0) and (1,0) when a bead $i$ is fixed, and then, to realize (b) and (e) in Fig.~\ref{fig:3bonds}. (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.

>>>>

There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. There are beads having a free hand at (1,0) and (-1,0) to realize (b) and (e) in Fig.~\ref{fig:3bonds} before bead $i-1$ is fixed at (0,0). One of these two beads may be a predecessor of bead $i-1$, but at least one bead is not. A bead $i-1$ makes a hydrogen bond with one of these two beads which is not its predecessor when it is fixed at (0,0). That is, it is impossible to put three beads having a free hand at (-1,0), (0,0) and (1,0) when a bead $i$ is fixed, and then, to realize (b) and (e) in Fig.~\ref{fig:3bonds}. (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.
